Enhance Road Detection Data Processing of LiDAR Point Clouds to Specifically Identify Unmarked Gravel Rural Roads

### 2023-08-17 Huston_Paper.tex
081620203

			{Manually defined areas were then overlayed onto the point cloud, representing training areas (Fig. \ref{fig:test_vs_train_areas}). Six degree arcs (Fig. \ref{fig:area_example}) from the first three channels of scanning LiDAR data centered directly in front of the vehicle were extracted and exported to a database if coincident with the manually defined areas. Later, nine arcs (three arcs from three channels) will be classified for the prediction of intersecting roads. Arc length was chosen based on approximate vehicle width (set to 6 degrees), and the location of each arc was fixed relative to the center line (length-wise) of the vehicle. Training data was extracted from a single arc, with approximately 28 LiDAR points per arc, from each 360 degree LiDAR scan if the arc was coincident to a manually projected 2D area. As arc is fixed to 6 degrees, the number of data points is constant, thus the only factor contributing to point density would be potential elevation changes between the vehicle and arc. This study found that the training data sparsity had a standard deviation that was distinct between LiDAR channels and similar between terrain classes in each LiDAR channel, therefore for this work LiDAR sparsity was considered a negligible issue. Raw spatial and intensity values from the coincident arc were saved to a raw training database. Separate training databases were maintained for each individual channel. Features that describe the raw spatial and intensity data were extracted. Thirty percent of the training data base was randomly selected and set aside as a validation data base. Training data was visually examined for clustering to verify that a RDF would be able to be trained (Fig. \ref{fig:training_data_cluster_2}). It was found that each class generally clustered to a certain range with some overlap, which indicates that a RDF may be trained. }

@@

		{Training and verification LiDAR, GPS, and IMU data collection was completed using the Experimental Apparatus. Gravel data was gathered from the Redmen Lodge gravel parking lot, while grass data was gathered beside the lot. Asphalt data was gathered Blackburn Road. Found research did not make any conclusive arguments for the proper training data set size for Random Decision Forest training; however, for this study the algorithm that produced the final results used multiple thousands of data sets. Results were then compared to algorithms trained with smaller data sets. Training data was generated using MATLAB to extract LiDAR data from rosbags, and RDF classification algorithms were generated. Testing consecutive scans was completed by post processing rosbags that contained scanning LiDAR, GPS, and IMU data. Physical distances between the GPS, IMU, and LiDAR were rectified by measuring the distance between the modules. Rotational reference frames between the GPS, IMU, and LiDAR were rectified by applying appropriate rotational matrices. Transformation matrices were created by considering the GPS position and the IMU's roll, pitch, and yaw data. Three scanning LiDAR arcs from three channels in front of the vehicle were classified. Translation and rotation was applied to the averaged x, y, and z coordinates of each arc's terrain classification results. Consecutive scanning LiDAR data was projected on manually classified truth areas representing road road surfaces (Figure \ref{fig:prepostadjust}) and percentages of terrain types per area were calculated.}

>>>>

			{Arcs of 6 degrees from the first three channels of scanning LiDAR data centered directly in front of the vehicle (Fig. \ref{fig:area_example}) were extracted and exported to a database if coincident with the manually defined areas (Fig. \ref{fig:test_vs_train_areas}). Later, nine arcs (three arcs from three channels) will be classified for the prediction of intersecting roads. Arc length was chosen based on approximate vehicle width (set to 6 degrees), and the location of each arc was fixed relative to the center line (length-wise) of the vehicle. Training data was extracted from a single arc, with approximately 28 LiDAR points per arc, from each 360 degree LiDAR scan if the arc was coincident to a manually projected 2D area. As arc is fixed to 6 degrees, the number of data points is constant, thus the only factor contributing to point density would be potential elevation changes between the vehicle and arc. This study found that the training data sparsity had a standard deviation that was distinct between LiDAR channels and similar between terrain classes in each LiDAR channel, therefore for this work LiDAR sparsity was considered a negligible issue. Raw spatial and intensity values from the coincident arc were saved to a raw training database. Separate training databases were maintained for each individual channel. Features that describe the raw spatial and intensity data were extracted. Thirty percent of the training data base was randomly selected and set aside as a validation data base. Training data was visually examined for clustering to verify that a RDF would be able to be trained (Fig. \ref{fig:training_data_cluster_2}). It was found that each class generally clustered to a certain range with some overlap, which indicates that a RDF may be trained. }

@@

		{Training and verification LiDAR, GPS, and IMU data collection was completed using the Experimental Apparatus. Gravel data was gathered from the Redmen Lodge gravel parking lot, while grass data was gathered beside the lot. Asphalt data was gathered Blackburn Road. Found research did not make any conclusive arguments for the proper training data set size for Random Decision Forest training; however, for this study the algorithm that produced the final results used multiple thousands of data sets per class. Results were compared to algorithms trained with smaller data sets, OH YEAH WHERE'S THE PROOF HONEY?. Training data was generated using MATLAB to extract LiDAR data from rosbags, and RDF classification algorithms were generated. Testing consecutive scans was completed by post processing rosbags that contained scanning LiDAR, GPS, and IMU data. Physical distances between the GPS, IMU, and LiDAR were rectified by measuring the distance between the modules. Rotational reference frames between the GPS, IMU, and LiDAR were rectified by applying appropriate rotational matrices. Transformation matrices were created by considering the GPS position and the IMU's roll, pitch, and yaw data. Three scanning LiDAR arcs from three channels in front of the vehicle were classified. Translation and rotation was applied to the averaged x, y, and z coordinates of each arc's terrain classification results. Consecutive scanning LiDAR data was projected on manually classified truth areas representing road road surfaces (Figure \ref{fig:prepostadjust}) and percentages of terrain types per area were calculated.}
